---
title: "MATH 201. Statistics I"
format: 
  html:
    toc: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Course Description

This course both satisfies the Quantitative Reasoning Requirement in the General Education Curriculum and serves as a foundational course for other mathematics courses.

A.  Connection to General Education:

-   Skills

    -   Ethical Engagement: Critical Thinking, Creative Thinking, Problem-Solving
    -   Engagement with Information: Data Analysis

-   UN Sustainable Development Goals (SDGs) focused upon:

    - #7 Affordable and Clean Energy
    - #9 Industry, Innovation, and Infrastructure
    - #11 Sustainable Cities and Communities


B. Mathematical Focus

In this course, students are taught the concepts necessary for data and statistical analysis and inference, in the context of real-world-type data analysis and modeling. Topics include data exploration, data visualization, descriptive statistics, classical probability, probability distributions, confidence intervals, and hypothesis testing,simple linear regression, and correlation. 


## Textbook

-   Bluman, Allan G. “Elementary Statistics: A Step by Step Approach : A Brief Version” Eighth
edition, McGraw-Hill Education Publishing. ISBN 978–0–07–338610–2


## Course Objectives

After successfully completing this course, the students can

- implement data visualization and data exploration techniques.
- explain the sampling approach in statistical inference.
- run and explain the results of common statistical hypothesis tests. 
- run and explain the results of linear regressions.
- compute confidence intervals for common parameters. 

## Grades


```{r}
# install.packages("ggplot2")
library(ggplot2)
library(dplyr)
# Variables

Percentage = c(.05, .1, .6, .25)
Grades = c('Attendance', 'Assignments','Midterm - Exams', 'Final Exam')

df = data.frame(Grades = Grades, Percentage = Percentage, labels = paste0(Percentage*100, "%"))

ggplot(df, aes(x = "", y = Percentage, fill = Grades)) +
  geom_col() +
  geom_label(aes(label = labels),
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  labs(x='')+
  coord_polar(theta = "y")+
  theme_void()
```

-  *Midterm Exams*: Tentatively, there are three Midterm exams, and each is worth 20%. A formula sheet (1 page) is allowed or included in the exam. Makeup exam will only be given to students who provide a valid written excuse BEFORE the date of the exam. The approved makeup exam should be taken no later than a week after the actual one. The grades posted on Canvas are official, and permanent after a week they are posted. The problems in the exams will be similar to those in the assignments and practice exams.

-   *Assignments*: Most of the assignments will be given and graded in class.

-   *Attendance*: Attendance will be checked regularly in class. Missing fewer than three classes will  The grade for attendance (5%) is enough to move up a letter grade. You are responsible for obtaining course material missed during an absence. 

## Exam Policies:

- All students are expected to be prepared for and take the assessment in class on the day it is
given.

- You must contact me by email before the assessment if you will not be present for the
assessment. Failure to notify me before the scheduled assessment will result in revocation of
the privilege to a make-up quiz/exam. The format of the make-up quiz/exam may be different
from the original quiz/exam.

- All quiz/exams must be made-up within one week of the day it was originally given.

## Excel 

We will be using Excel to build on topics we will be learning in class. Excel is located on your
Bryant issued laptop. Please access Excel before our first use to make sure there are no issues. If there
are, please bring your laptop to the Help Desk or Laptop Central. It is expected that you bring your
fully charged laptop to class on Excel days (denoted in the course schedule). Please bring your Bryant
issued laptop these days as Macs have different directions and slow the process of a whole class
activity.

## Calculator 

A scientific calculator is required for this course and should be brought to class every
day. A calculator is needed for every exam and
quiz in this course.

## Cell Phones 

Cell phone use during class is strongly discouraged. Cell phone use during an exam
is prohibited. It cannot be used as a calculator. Use of cell phones or any electronic device during
an assessment will result in a score of “0” for that assessment.

## Grades Scale

The numerical grades are converted to letter grades as follows.

|     |                |     |                |
|-----|----------------|-----|----------------|
| A   | 92.45 - 100%   | C   | 72.45 - 76.44% |
| A-  | 89.45 - 92.44% | C-  | 69.45 - 72.44% |
| B+  | 86.45 - 89.44% | D+  | 66.45 - 69.44% |
| B   | 82.45 - 86.44% | D   | 59.45 - 66.44% |
| B-  | 79.45 - 82.44% | F   | Below 59.44%   |
| C+  | 76.45 - 79.44% |     |                |

```{r}
library(ggplot2)
library(forcats)

# Basic barplot

Grades           = c("A","A-","B+","B","B-","C+","C","C-","D+","D", "F")
Total_Percentage = c(92.45, 89.45, 86.45, 82.45 ,79.45, 76.45, 72.45, 69.45, 66.45, 59.45, 0)
df = data.frame(Grades = Grades, Total_Percentage = Total_Percentage)


p<-ggplot(data=df, aes(x= fct_rev(fct_reorder(Grades, Total_Percentage)), y=Total_Percentage)) +
  geom_col(fill="steelblue")+
  labs(y = 'Total Percentage', x ='Letter Grade')+
  geom_text(aes(label = Total_Percentage), vjust = -0.5)+
  theme_minimal()
p

```

## Tentative Topics

-   Data Exploration and Visualization
-   Sampling Approach
-   Hypothesis Testing
-   Data Simulation
-   Linear Regression

## Sustainable Development Goals

We will occasionally discuss and work with data related to the [United Nation Sustainable Development Goals](https://sdgs.un.org/goals). These goals are called by the UN for action in a global partnership to provide peace and prosperity for people and the planet, now and into the future. Specifically, we will focus one of the following three SDGs:

-   [SDG 7 - Affordable and Clean Energy](https://www.globalgoals.org/goals/7-affordable-and-clean-energy/)
-   [SDG 9 - Affordable and Clean Energy](https://www.globalgoals.org/goals/9-industry-innovation-and-infrastructure/)
-   [SDG 11 - Sustainable Cities and Communities](https://www.globalgoals.org/goals/11-sustainable-cities-and-communities/)

## Academic Misconduct

Cheating will result in an F as your final grade and may result in your expulsion from the University. All cheating will be reported to the Chair of the Mathematics Department and Academic Advising.

## Regarding Diversity

In this course, and all your courses at Bryant, and throughout the Bryant learning community, we value and respect diversity. This includes differences in race, ethnicity, nationality, gender, gender identity, sexuality, socioeconomic status, ability, and religion.
