---
title: "MATH 201. Statistics I"
format: 
  html:                                                                                                                                                                                                                                                   
    toc: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


## Course Description

This course both satisfies the Quantitative Reasoning Requirement in the General Education Curriculum and serves as a foundational course for other mathematics courses.

A.  Connection to General Education:

-   Skills

    -   Ethical Engagement: Critical Thinking, Creative Thinking, Problem-Solving
    -   Engagement with Information: Data Analysis

-   UN Sustainable Development Goals (SDGs) focused upon:

    - #7 Affordable and Clean Energy
    - #9 Industry, Innovation, and Infrastructure
    - #11 Sustainable Cities and Communities


B. Mathematical Focus

In this course, students are taught the concepts necessary for data and statistical analysis and inference, in the context of real-world-type data analysis and modeling. Topics include data exploration, data visualization, descriptive statistics, classical probability, probability distributions, confidence intervals, and hypothesis testing,simple linear regression, and correlation. 


## Textbook

-   No text books required

## Course Objectives

After successfully completing this course, the students can

- implement data visualization and data exploration techniques.
- explain the sampling approach in statistical inference.
- run and explain the results of common statistical hypothesis tests. 
- run and explain the results of linear regressions.
- compute confidence intervals for common parameters. 

## Grades

```{r}
# install.packages("ggplot2")
library(ggplot2)
library(dplyr)
# Variables

Percentage = c(.7,.3)
Grades = c('Assignments','Attendance')

df = data.frame(Grades = Grades, Percentage = Percentage, labels = paste0(Percentage*100, "%"))

ggplot(df, aes(x = "", y = Percentage, fill = Grades)) +
  geom_col() +
  geom_label(aes(label = labels),
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  labs(x='')+
  coord_polar(theta = "y")+
  theme_void()
```

-   *Assignments*: Tentatively, the assignments and case studies will be done during class where you can ask questions.

-   *Attendance*: The class have totally 15 meetings. Each time you attend a meeting, your total grade will be increased by 1.5%.

## Grades Scale

The numerical grades are converted to letter grades as follows.

|     |                |     |                |
|-----|----------------|-----|----------------|
| A   | 92.45 - 100%   | C   | 72.45 - 76.44% |
| A-  | 89.45 - 92.44% | C-  | 69.45 - 72.44% |
| B+  | 86.45 - 89.44% | D+  | 66.45 - 69.44% |
| B   | 82.45 - 86.44% | D   | 59.45 - 66.44% |
| B-  | 79.45 - 82.44% | F   | Below 59.44%   |
| C+  | 76.45 - 79.44% |     |                |

```{r}
library(ggplot2)
library(forcats)

# Basic barplot

Grades           = c("A","A-","B+","B","B-","C+","C","C-","D+","D", "F")
Total_Percentage = c(92.45, 89.45, 86.45, 82.45 ,79.45, 76.45, 72.45, 69.45, 66.45, 59.45, 0)
df = data.frame(Grades = Grades, Total_Percentage = Total_Percentage)


p<-ggplot(data=df, aes(x= fct_rev(fct_reorder(Grades, Total_Percentage)), y=Total_Percentage)) +
  geom_col(fill="steelblue")+
  labs(y = 'Total Percentage', x ='Letter Grade')+
  geom_text(aes(label = Total_Percentage), vjust = -0.5)+
  theme_minimal()
p

```

## Tentative Topics

-   Data Exploration and Visualization
-   Sampling Approach
-   Hypothesis Testing
-   Data Simulation
-   Linear Regression

## Sustainable Development Goals

We will occasionally discuss and work with data related to the [United Nation Sustainable Development Goals](https://sdgs.un.org/goals). These goals are called by the UN for action in a global partnership to provide peace and prosperity for people and the planet, now and into the future. Specifically, we will focus one of the following three SDGs:

-   [SDG 7 - Affordable and Clean Energy](https://www.globalgoals.org/goals/7-affordable-and-clean-energy/)
-   [SDG 9 - Affordable and Clean Energy](https://www.globalgoals.org/goals/9-industry-innovation-and-infrastructure/)
-   [SDG 11 - Sustainable Cities and Communities](https://www.globalgoals.org/goals/11-sustainable-cities-and-communities/)

## Academic Misconduct

Cheating will result in an F as your final grade and may result in your expulsion from the University. All cheating will be reported to the Chair of the Mathematics Department and Academic Advising.

## Regarding Diversity

In this course, and all your courses at Bryant, and throughout the Bryant learning community, we value and respect diversity. This includes differences in race, ethnicity, nationality, gender, gender identity, sexuality, socioeconomic status, ability, and religion.
